Climate-RWI relations

### 2018-01-25 analysis/rwi/climate_rwi_relate.Rmd
update rwi climate with selected monts

---
title: "Climate-RWI relations"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output:
  md_document:
    variant: markdown_github
bibliography: ../refs/references.bib 
csl: ../refs/ecology.csl
---

@@

```{r}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')
```

@@

rprec_all <- rprec_all %>% 
  mutate(month_name = case_when(
      month == "sep...AUG" ~ "Hydrol", 
      TRUE ~ as.character(.$month)))
```

@@

rspei_all <- customNames(rspei_all) 
```

@@

rsequia_all <- customNames(rsequia_all) 
```

@@

rtmean_all <- customNames(rtmean_all) 
```

@@

# Rename variable 
rtmin_all <- customNames(rtmin_all) 
```

@@

# Rename variable 
rtmax_all <- customNames(rtmax_all) 
```

>>>>

---
title: "Climate-RWI relations"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output:
  md_document:
    variant: markdown_github
bibliography: ../../refs/references.bib 
csl: ../../refs/ecology.csl
---

@@

```{r}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')
```

@@

write.csv(rprec_all, here("/data/rwi_climate", "rprec_all.csv"), row.names = FALSE)
```

@@

rspei_all <- customNames(rspei_all)

write.csv(rspei_all, here("/data/rwi_climate", "rspei_all.csv"), row.names = FALSE)
```

@@

rsequia_all <- customNames(rsequia_all)

write.csv(rsequia_all, here("/data/rwi_climate", "rsequia_all.csv"), row.names = FALSE)
```

@@

rtmean_all <- customNames(rtmean_all) 
write.csv(rtmean_all, here("/data/rwi_climate", "rtmean_all.csv"), row.names = FALSE)
```

@@

# Rename variable 
rtmin_all <- customNames(rtmin_all) 
write.csv(rtmin_all, here("/data/rwi_climate", "rtmin_all.csv"), row.names = FALSE)
```

@@

# Rename variable 
rtmax_all <- customNames(rtmax_all) 
write.csv(rtmax_all, here("/data/rwi_climate", "rtmax_all.csv"), row.names = FALSE)
```
